### 2018-10-28 Sections/economics_of_the_quantum_internet.tex
minor

We will now treat some of these economic issues in the context of a global network of unified quantum computing resources, which are then equitably time-shared\index{Time-sharing}. We argue in Sec.~\ref{sec:time_share} that this time-shared model for quantum computation is always more computationally efficient than having distinct quantum computers operating independently in parallel, owing to the super-linear scaling in their joint computational power. While this section provides mathematical details of various economic models, Secs.~\ref{sec:economics} \& \ref{sec:quant_coin_essay} provide a popular, high-level discussion surrounding these issues.

@@

Since exisiting network participants receive leverage upon other participants joining the network, an investment into contributing modules has monotonically increasing computational return over time as the network expands, even if that participant ceases making further investment into the network. This is in contrast to classical networks, whereby the computational return upon an investment is fixed over time.

To formalise this, consider the case where a user purchases an initial single qubit \mbox{$n_\mathrm{user}=1$}, while the global network expands over time as \mbox{$n_\mathrm{global}=N_t$}. Then the classical-equivalent computational power of the user is,

\begin{definition}[Static computational return]\index{Static computational return} The static (i.e fixed-investment) computational return is the classical-equivalent processing power of a user's time-share, where the user has a fixed investment of one qubit, whereas the network is allowed to expand over time arbitrarily,
\begin{align}
	r_\mathrm{static}(t) &= \frac{f_\mathrm{sc}(N_t)}{N_t}\nonumber\\
	&= \chi_\mathrm{sc}(N_t),
\end{align}
which is equivalent to the collective per-qubit computational power of the entire network.
\end{definition}

Examples for this relationship are equivalent to those presented earlier in Fig.~\ref{fig:NPSF}.

@@

\section{Summary of economic models}

>>>>

We will now treat some of these economic issues in the context of a global network of unified quantum computing resources, which are then equitably time-shared\index{Time-sharing}. We argue in Sec.~\ref{sec:time_share} that this time-shared model for quantum computation is always more computationally efficient than having distinct quantum computers operating independently in parallel, owing to the super-linear scaling in their joint computational power. While this section provides mathematical details of various economic models, Secs.~\ref{sec:economics} \& \ref{sec:quant_coin_essay} provide a popular, high-level discussion surrounding these issues. Sec.~\ref{sec:summary_economic_models} summarises the various economic models we present in this part.

@@

Since exisiting network participants receive leverage upon \textit{other} participants joining the network, an investment into contributing modules has monotonically increasing computational return over time as the network expands, even if that participant ceases making further investment into the network. This is in contrast to classical networks, whereby the computational return upon an investment is fixed over time.

To formalise this, consider the case where a user purchases an initial single qubit \mbox{$n_\mathrm{user}=1$}, while the global network expands over time as \mbox{$n_\mathrm{global}=N_t$}. Then the classical-equivalent computational power of the user's fixed investment is,

\begin{definition}[Static computational return]\index{Static computational return} The static computational return is the classical-equivalent processing power of a user's time-share, where the user has a fixed investment of one qubit, whereas the network is allowed to expand over time arbitrarily (e.g according to a quantum Moore's Law),
\begin{align}
	r_\mathrm{static}(t) &= \frac{f_\mathrm{sc}(N_t)}{N_t}\nonumber\\
	&= \chi_\mathrm{sc}(N_t),
\end{align}
which is equivalent to the collective per-qubit computational power of the entire network.
\end{definition}

Graphical examples for this relationship are equivalent to those presented earlier in Fig.~\ref{fig:NPSF}.

@@

\section{Summary of economic models}\index{Summary of economic models}\label{sec:summary_economic_models}
